Laplacian envelope

### 2021-07-27 Notes/laplace.tex
using property.setter in options
tex problems
typos

\newcommand{\aav}[1]{\mathopen{}\left\lAngle #1 \right\rAngle\mathclose{}}
\newcommand{\nnrm}[1]{\mathopen{}\left\lVvert #1 \right\rVvert\mathclose{}}
%================================================================================
%
\usepackage{adjustbox}
\newcommand{\aligntop}[1]{\adjustbox{valign=t}{#1}}
\newcommand{\alignmid}[1]{\adjustbox{valign=c}{#1}}
%
\usepackage{paralist}
\newenvironment{myenuma}{\begin{inparaenum}[(a)]}{\end{inparaenum}}
\newenvironment{myenumi}{\begin{inparaenum}[i)]}{\end{inparaenum}}
\newenvironment{myenumA}{\begin{inparaenum}[\bfseries A.]}{\end{inparaenum}}
\newenvironment{myenumI}{\begin{inparaenum}[\bfseries I.]}{\end{inparaenum}}
\newenvironment{myenumr}{\begin{inparaenum}[1.]}{\end{inparaenum}}
%for nested lists, \ref only produces innermost item:  (hacky)
\makeatletter % for internal macros with @
\renewcommand\p@enumii{}
\makeatother
%
%================================================================================
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MMm}{Q}
\newcommand{\MM}{\mathbf{\MMm}}
%prob distribution
\newcommand{\prm}{p}
\newcommand{\pr}{\mathbf{\prm}}
%equilibrium distribution
\newcommand{\eqm}{\pi}
\newcommand{\eq}{\boldsymbol{\eqm}}
%equilibrium metric
\newcommand{\Eqm}{\Pi}
\newcommand{\Eq}{\boldsymbol{\Eqm}}
%first passage times
\newcommand{\fptm}{T}
\newcommand{\fpt}{\mathbf{\fptm}}
%off-diag first passage times
\newcommand{\fptbm}{\overline{\fptm}}
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fundm}{Z}
\newcommand{\fund}{\mathbf{\fundm}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arowm}{\xi}
\newcommand{\arow}{\boldsymbol{\arowm}}
\newcommand{\Lbm}{\Lambda}
\newcommand{\Lb}{\boldsymbol{\Lbm}}
\newcommand{\lbm}{\lambda}
\newcommand{\lb}{\boldsymbol{\lbm}}
\newcommand{\etwm}{\eta^w}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thbm}{\theta}
\newcommand{\thb}{\boldsymbol{\thbm}}
\newcommand{\ombm}{\omega}
\newcommand{\omb}{\boldsymbol{\ombm}}
\newcommand{\albm}{\alpha}
\newcommand{\alb}{\boldsymbol{\albm}}
%synapse models
\newcommand{\wm}{w}
\newcommand{\w}{\mathbf{\wm}}
\newcommand{\Wm}{W}
\newcommand{\W}{\mathbf{\Wm}}
\newcommand{\MMdm}{M}
\newcommand{\MMd}{\mathbf{\MMdm}}
\newcommand{\encm}{K}
\newcommand{\enc}{\mathbf{\encm}}
\newcommand{\frgm}{\Wm^{\mathrm{F}}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\Fm}{\Phi}
\newcommand{\F}{\boldsymbol{\Fm}}
%eigenvectors
\newcommand{\evrm}{u}
\newcommand{\evr}{\mathbf{\evrm}}
\newcommand{\evlm}{\eta}
\newcommand{\evl}{\boldsymbol{\evlm}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
% \newcommand{\CA}{\mathcal{A}}
% \newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \e^{rt\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \e^{rt\frg} \w .
\end{aligned}
\end{equation}
%
Combining these allows us to write the numerator of \eqref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= N \eq \enc \, \e^{rt \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu f^\nu (\MMd^\nu - \I)
    = f\pot(\MMd \pot-\I)-f\dep(\MMd \dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{rt \frg}\w}
                 {\sqrt{1-(f\pot-f\dep)^2(\eq \w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with \(f\pot=f\dep\) or \(\eq_+=\eq_-\).
We can perform the maximisation in two steps.
First maximise the numerator at fixed \(\eq \w\).
Then maximise the ratio \wrt \(\eq\w\).
This will allow us to ignore the denominator until the very end.

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s \I + \onev \arow -\MM)\inv,
\end{equation}
%
where \(\arow\) is an arbitrary row vector satisfying \(\arow \onev = \frac{1}{\tau_0} \neq 0\).
This reduces to the fundamental matrix at \(s=0\).
We can see that \(\onev\) is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau_0}{1+s\tau_0}\onev.
\end{equation}
%
Suppose we have some row vector \(\mathbf{a}\) such that \(\mathbf{a}\onev=0\).
Then \(\mathbf{a}\fund(s)\) is independent of \(\arow\):
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\arowm_k} = -(\mathbf{a}\fund(s)\onev) \fundm_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fundm_{ki}(s) = 0.
\end{equation}
%

@@

At other values of \(s\) can they be interpreted as the mean first-passage times of a different process?
In order to have \cref{eq:lfund} as its fundamental matrix, the extra bit must draw probability from each state at a rate \(s\).
In other words, it should have the form \(s(\onev \boldsymbol{\zeta} - \I)\) for some \(\boldsymbol{\zeta} \) 
(which can be absorbed into \(\arow\) in \cref{eq:lfund}).
This other process must have the same steady-state distribution, so that its mean first-passage times are given by \cref{eq:lfptb}, so the probability drawn from each state must be redistributed proportional to \(\eq\).
This other stochastic process is
%
\begin{equation}\label{eq:lshift}
  \shift{\MM}(s) = \MM + s (\onev \eq - \I).
\end{equation}
%
This is a valid continuous-time Markov process.
Its fundamental matrix is given by \cref{eq:lfund} with \( \arow_0 = \arow + s \eq \).

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }
                                { \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s \I - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at \(s=0\).
Thanks to \eqref{eq:alfund}, we can solve this by the replacement \(\mathbf{G}(s) \to \fund(s)\), as \(\enc\onev=0\).
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)} \eqm_k \wm_k \\
    &= \sum_{ij}  \eqm_i \encm_{ij} (\etwm_{i}(s) - \etwm_{j}(s)).
\end{aligned}
\end{equation}
%
Note that \(A(0)=A\), the area, and \(\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)\), the initial SNR.

@@

This allows us to calculate the $c_k$'s:
%
\begin{equation}\label{eq:serialareacoeff}
\begin{aligned}
  c_k &= \sum_{i<k} \fptbm_{i,i+1} \prn{\eqm_{i} f\pot q\pot_i + \eqm_{i+1} f\dep q\dep_i}
    %\\&
    - \sum_{i\geq k} \fptbm_{i+1,i} \prn{\eqm_{i} f\pot q\pot_i + \eqm_{i+1} f\dep q\dep_i}
  ,\\
  c_{k+1} - c_k &= \prn{\fptbm_{k,k+1} + \fptbm_{k+1,k}} \prn{\eqm_{k} \frgm_{k,k+1} + \eqm_{k+1} \frgm_{k+1,k}}
    =%\\=&\,
    \frac{2}{r},\\
  \sum_k c_k \eqm_k &= \sum_{ij} \eqm_i \encm_{ij} (\eta-\eta) = 0,\\
%  \implies c_k =&\, \frac{\prn{k-\frac{n+1}{2}} - \sum_j\prn{j-\frac{n+1}{2}}\eq_j}{f^+f^-},
  \implies c_k &= \frac{2}{r} \prn{k - \sum_j j\eqm_j},
\end{aligned}
\end{equation}
%
where we used \cref{eq:serialineq} to derive the first two equations respectively and \cref{eq:lkemeny} to derive the third. 
This allows us to write the area as
%
\begin{equation}\label{eq:serialarea}
 % A = 2\sqrt{N} \sum_k \brk{\prn{k-\frac{n+1}{2}} - \sum_j\prn{j-\frac{n+1}{2}}\eq_j} \eq_k \w_k.
  \CA = \frac{2}{r} \sum_k \brk{k - \sum_j j\eq_j} \eqm_k \wm_k
    = \frac{2}{r} \sum_k \abs{k - \sum_j j\eq_j} \eqm_k ,
\end{equation}
%
where we used $\wm_k=\sgn(c_k)$, as discussed after \cref{eq:lareacoeffs}.

First let us maximise \cref{eq:serialarea} at fixed $\eqm_\pm = \sum_k \eqm_k \prn{\frac{1\pm\wm_k}{2}}$.
Clearly this will happen when we put all of the probability at the ends: $\eqm_1=\eqm_-$ and $\eqm_n=\eqm_+$ are the only non-zero $\eqm_k$.
This gives an area of
\footnote{Note that including the dropped factors in \cref{eq:lsnr} would only change this to \(\CA \leq (M-1)(4\eq_+\eq_-)/r\sqrt{1 - (f\pot-f\dep)^2(\eqm_+ - \eqm_-)^2}\), whose maximum also lies at \(\eqm_+=\eqm_-= \frac{1}{2}\).}
%
\begin{equation}\label{eq:serialextarea}
  \CA \leq \frac{(M-1)}{r}\prn{4\eqm_+\eqm_-}.
\end{equation}
%
This is maximised at \(\eqm_+=\eqm_-= \frac{1}{2}\):
%
\begin{equation}\label{eq:maxarea}
  \CA \leq \frac{(M-1)}{r}.
\end{equation}
%
Note that the markov process that achieves this is not ergodic, the two states at each end are absorbing. 
This is similar to the results found numerically in \cite{Barrett2008discrete} in a slightly different situation.

@@

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:lshiftderivs}
\begin{aligned}
  \frac{1}{f^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m - \thbm_n}
     + \prn{{c}_m + (-1)^\nu + \lambda} \brk{\etwm_m - \etwm_n} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     - \sum_{ij} \mu^\nu_{ij} s f^\nu \eqm_m (\fptbm_{mj} - \fptbm_{nj}) \eqm_j
    = 0.
\end{aligned}
\end{equation}
%
We can absorb the new terms by defining
%
\begin{equation*}
\begin{aligned}
  \shift{\thb}^\nu(s) = \thb(0) - s f^\nu \fptb(0) \Eq (\boldsymbol{\mu}^\nu)\trans \onev,
  \qquad
  \shift{\alb}^\nu(s) &= (\MMd^\nu + (s - 1) \I - s \onev \eq) \shift{\thb}^\nu(s),
  \\
  \shift{\omb}^\nu(s) &= (\MMd^\nu + (s - 1) \I - s \onev \eq) \etw(0).
\end{aligned}
\end{equation*}
%
We note that
%
\begin{equation*}
  \mu^\nu_{ij} (\MMdm^\nu_{ij} - s \eqm_j) = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} (\MMdm^\nu_{ij} - s \eqm_j)
      = \mu^\nu_{ii} (1 - \MMdm^\nu_{ii} - s (1 - \eqm_i)) = \mu^\nu_{ii},
\end{equation*}
%
then we can ``solve'' for the KKT multipliers:
%
\begin{equation}\label{eq:lshiftsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \shift{\albm}^\nu_m(s) 
    + \brk{ {c}_m + (-1)^\nu + \lambda } \shift{\ombm}^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \prn{ 
      \brk{ \shift{\thbm}^\nu_n(s) - \shift{\thbm}^\nu_m(s) - \shift{\albm}^\nu_m(s) }
  % \\ & \phantom{= - \eqm_m \big( } 
    + \brk{ {c}_m + (-1)^\nu + \lambda } 
        \brk{ \etwm_n - \etwm_m - \shift{\ombm}^\nu_m(s) }
     }, \\
\end{aligned}
\end{equation}
%
although there are KKT multipliers hiding in \(\shift{\thb}^\nu(s)\) and \(\shift{\alb}^\nu(s)\).

>>>>

\newcommand{\aav}[1]{\mathopen{}\left\lAngle #1 \right\rAngle\mathclose{}}
\newcommand{\nnrm}[1]{\mathopen{}\left\lVvert #1 \right\rVvert\mathclose{}}
%================================================================================
%
% \usepackage{adjustbox}
% \newcommand{\aligntop}[1]{\adjustbox{valign=t}{#1}}
% \newcommand{\alignmid}[1]{\adjustbox{valign=c}{#1}}
%
\usepackage{paralist}
\newenvironment{myenuma}{\begin{inparaenum}[(a)]}{\end{inparaenum}}
\newenvironment{myenumi}{\begin{inparaenum}[i)]}{\end{inparaenum}}
\newenvironment{myenumA}{\begin{inparaenum}[\bfseries A.]}{\end{inparaenum}}
\newenvironment{myenumI}{\begin{inparaenum}[\bfseries I.]}{\end{inparaenum}}
\newenvironment{myenumr}{\begin{inparaenum}[1.]}{\end{inparaenum}}
%for nested lists, \ref only produces innermost item:  (hacky)
\makeatletter % for internal macros with @
\renewcommand\p@enumii{}
\makeatother
%
%================================================================================
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MMm}{Q}
\newcommand{\MM}{\mathbf{\MMm}}
%prob distribution
\newcommand{\prm}{p}
\newcommand{\pr}{\mathbf{\prm}}
%equilibrium distribution
\newcommand{\eqm}{\pi}
\newcommand{\eq}{\boldsymbol{\eqm}}
%equilibrium metric
\newcommand{\Eqm}{\Pi}
\newcommand{\Eq}{\boldsymbol{\Eqm}}
%first passage times
\newcommand{\fptm}{T}
\newcommand{\fpt}{\mathbf{\fptm}}
%off-diag first passage times
\newcommand{\fptbm}{\overline{\fptm}}
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fundm}{Z}
\newcommand{\fund}{\mathbf{\fundm}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arowm}{\xi}
\newcommand{\arow}{\boldsymbol{\arowm}}
\newcommand{\Lbm}{\Lambda}
\newcommand{\Lb}{\boldsymbol{\Lbm}}
\newcommand{\lbm}{\lambda}
\newcommand{\lb}{\boldsymbol{\lbm}}
\newcommand{\etwm}{\eta^w}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thbm}{\theta}
\newcommand{\thb}{\boldsymbol{\thbm}}
\newcommand{\ombm}{\omega}
\newcommand{\omb}{\boldsymbol{\ombm}}
\newcommand{\albm}{\alpha}
\newcommand{\alb}{\boldsymbol{\albm}}
%synapse models
\newcommand{\wm}{w}
\newcommand{\w}{\mathbf{\wm}}
\newcommand{\Wm}{W}
\newcommand{\W}{\mathbf{\Wm}}
\newcommand{\MMdm}{M}
\newcommand{\MMd}{\mathbf{\MMdm}}
\newcommand{\encm}{K}
\newcommand{\enc}{\mathbf{\encm}}
\newcommand{\frgm}{\Wm^{\mathrm{F}}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\Fm}{\Phi}
\newcommand{\F}{\boldsymbol{\Fm}}
%eigenvectors
\newcommand{\evrm}{u}
\newcommand{\evr}{\mathbf{\evrm}}
\newcommand{\evlm}{\eta}
\newcommand{\evl}{\boldsymbol{\evlm}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
% \newcommand{\CA}{\mathcal{A}}
% \newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \e^{rt\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  \Delta f\, \eq \e^{rt\frg} \w ,
\end{aligned}
\end{equation}
%
where \(\Delta f = f\pot - f\dep \).
Combining the expressions in \cref{eq:overlapwt} allows us to write the numerator of \cref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= N \eq \enc \, \e^{rt \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu f^\nu (\MMd^\nu - \I)
    = f\pot(\MMd \pot-\I)-f\dep(\MMd \dep-\I)
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{rt \frg}\w}
                 {\sqrt{1-(\Delta f)^2(\eq \w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with \(f\pot=f\dep\) or \(\eq_+=\eq_-\).
We can perform the maximisation in two steps.
First maximise the numerator at fixed \(\eq \w\).
Then maximise the ratio \wrt \(\eq\w\).
This will allow us to ignore the denominator until the very end.

@@

In analogy to the generalised fundamental matrix of a Markov chain \cite{Kemeny1981fund}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s \I + \onev \arow -\MM)\inv,
\end{equation}
%
where \(\arow\) is an arbitrary row vector satisfying \(\arow \onev = \frac{1}{\tau_0} \neq 0\).
This reduces to the fundamental matrix at \(s=0\).
We can see that it obeys similar identities, including that \(\onev\) is an eigenvector:
%
\begin{equation}\label{eq:lfundrowsum}
\begin{aligned}
  \fund(s) \onev &= \frac{\tau_0}{1+s\tau_0}\onev, \qquad &
  \MM \fund(s) &= (\onev \eq - \I)(\I - s \fund), \\ 
  \arow \fund(s) &= \eq (\I - s \fund),  &
  \fund(s) \MM &= (\I - s \fund)(\tau_0 \onev \arow - \I).
\end{aligned}
\end{equation}
%
Suppose we have some row vector \(\mathbf{a}\) such that \(\mathbf{a}\onev=0\).
Then \(\mathbf{a}\fund(s)\) is independent of \(\arow\):
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\arowm_k} = -(\mathbf{a}\fund(s)\onev) \fundm_{ki}(s)
      = -\frac{\tau_0}{1+s\tau_0} (\mathbf{a}\onev) \fundm_{ki}(s) = 0.
\end{equation}
%

@@

At other values of \(s\) can they be interpreted as the mean first-passage times of a different process?
In order to have \cref{eq:lfund} as its fundamental matrix, the extra bit must draw probability from each state at a rate \(s\).
In other words, it should have the form \(s(\onev \boldsymbol{\zeta} - \I)\) for some \(\boldsymbol{\zeta} \) 
(which can be absorbed into \(\arow\) in \cref{eq:lfund}).
This other process must have the same steady-state distribution, so that its mean first-passage times are given by \cref{eq:lfptb}, so the probability drawn from each state must be redistributed proportional to \(\eq\).
This other stochastic process is
%
\begin{equation}\label{eq:lshift}
  \shift{\MM}(s) = \MM + s (\onev \eq - \I).
\end{equation}
%
This is a valid continuous-time Markov process.
Its fundamental matrix is given by \cref{eq:lfund} with \( \arow(s) = \arow + s \eq \) (although this last change is unnecessary).

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }
                                { \sqrt{1-(\Delta f)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s \I - r\frg}\inv \w }{\sqrt{1-(\Delta f)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at \(s=0\).
Thanks to \eqref{eq:alfund}, we can solve this by the replacement \(\mathbf{G}(s) \to \fund(s)\), as \(\enc\onev=0\).
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(\Delta f)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)} \eqm_k \wm_k \\
    &= \sum_{ij}  \eqm_i \encm_{ij} (\etwm_{i}(s) - \etwm_{j}(s)).
\end{aligned}
\end{equation}
%
Note that \(A(0)=A\), the area, and \(\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)\), the initial SNR.

@@

This allows us to calculate the $c_k$'s from \cref{eq:lareacoeffs}:
%
\begin{equation}\label{eq:serialareacoeff}
\begin{aligned}
  c_k &= \sum_{i<k} \prn{\eqm_{i} f\pot q\pot_i + \eqm_{i+1} f\dep q\dep_i} \fptbm_{i,i+1}
    %\\&
    - \sum_{i\geq k} \prn{\eqm_{i} f\pot q\pot_i + \eqm_{i+1} f\dep q\dep_i} \fptbm_{i+1,i}
  ,\\
  c_{k+1} - c_k &= \prn{\eqm_{k} \frgm_{k,k+1} + \eqm_{k+1} \frgm_{k+1,k}}
                    \prn{\fptbm_{k,k+1} + \fptbm_{k+1,k}}
    = \frac{2}{r},\\
  \sum_k c_k \eqm_k &= \sum_{ij} \eqm_i \encm_{ij} (\eta-\eta) = 0,\\
  \implies c_k &= \frac{2}{r} \prn{k - \sum_j j\eqm_j},
\end{aligned}
\end{equation}
%
where we used \cref{eq:serialineq} to derive the first two equations respectively and \cref{eq:lkemeny} to derive the third. 
This allows us to write the area as
%
\begin{equation}\label{eq:serialarea}
 % A = 2\sqrt{N} \sum_k \brk{\prn{k-\frac{n+1}{2}} - \sum_j\prn{j-\frac{n+1}{2}}\eq_j} \eq_k \w_k.
  \CA = \frac{2}{r} \sum_k \brk{k - \sum_j j\eq_j} \eqm_k \wm_k
    = \frac{2}{r} \sum_k \abs{k - \sum_j j\eq_j} \eqm_k ,
\end{equation}
%
where we used $\wm_k=\sgn(c_k)$, as discussed after \cref{eq:lareacoeffs}.

First let us maximise \cref{eq:serialarea} at fixed $\eqm_\pm = \sum_k \eqm_k \prn{\frac{1\pm\wm_k}{2}}$.
Clearly this will happen when we put all of the probability at the ends: $\eqm_1=\eqm_-$ and $\eqm_n=\eqm_+$ are the only non-zero $\eqm_k$.
This gives an area of
\footnote{Note that including the dropped factors in \cref{eq:lsnr} would only change this to \(\CA \leq (M-1)(4\eq_+\eq_-)/r\sqrt{1 - (\Delta f)^2(\eqm_+ - \eqm_-)^2}\), whose maximum also lies at \(\eqm_+=\eqm_-= \frac{1}{2}\).}
%
\begin{equation}\label{eq:serialextarea}
  \CA \leq \frac{(M-1)}{r}\prn{4\eqm_+\eqm_-}.
\end{equation}
%
This is maximised at \(\eqm_+=\eqm_-= \frac{1}{2}\):
%
\begin{equation}\label{eq:maxarea}
  \CA \leq \frac{(M-1)}{r}.
\end{equation}
%
Note that the markov process that achieves this is not ergodic, the two states at each end are absorbing. 
This is similar to the results found numerically in \cite{Barrett2008discrete} in a slightly different situation.

@@

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:lshiftderivs}
\begin{aligned}
  \frac{1}{f^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m - \thbm_n}
     + \prn{{c}_m + (-1)^\nu + \lambda} \brk{\etwm_m - \etwm_n} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     - \sum_{\mu ij} \mu^\mu_{ij} s f^\mu \eqm_m (\fptbm_{mj} - \fptbm_{nj}) \eqm_j
    = 0.
\end{aligned}
\end{equation}
%
We can absorb the new terms by defining
%
\begin{equation*}
\begin{aligned}
  \shift{\thb}^\nu(s) = \thb(0) - s f^\nu \fptb(0) \Eq (\boldsymbol{\mu}^\nu)\trans \onev,
  \qquad
  \shift{\alb}^\nu(s) &= (\MMd^\nu + (s - 1) \I - s \onev \eq) \shift{\thb}^\nu(s),
  \\
  \shift{\omb}^\nu(s) &= (\MMd^\nu + (s - 1) \I - s \onev \eq) \etw(0).
\end{aligned}
\end{equation*}
%
We note that
%
\begin{equation*}
  \mu^\nu_{ij} (\MMdm^\nu_{ij} - s \eqm_j) = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} (\MMdm^\nu_{ij} - s \eqm_j)
      = \mu^\nu_{ii} (1 - \MMdm^\nu_{ii} - s (1 - \eqm_i)) = \mu^\nu_{ii},
\end{equation*}
%
then we can ``solve'' for the KKT multipliers:
%
\begin{equation}\label{eq:lshiftsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \shift{\albm}^\nu_m(s) 
    + \brk{ {c}_m + (-1)^\nu + \lambda } \shift{\ombm}^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \prn{ 
      \brk{ \shift{\thbm}^\nu_n(s) - \shift{\thbm}^\nu_m(s) - \shift{\albm}^\nu_m(s) }
  % \\ & \phantom{= - \eqm_m \big( } 
    + \brk{ {c}_m + (-1)^\nu + \lambda } 
        \brk{ \etwm_n - \etwm_m - \shift{\ombm}^\nu_m(s) }
     }, \\
\end{aligned}
\end{equation}
%
although there are KKT multipliers hiding in \(\shift{\thb}^\nu(s)\) and \(\shift{\alb}^\nu(s)\).
